### 2017-02-27 2017mergingmerges/section/05-Evaluation.tex
Rename file to 05-Evaluation.tex

% I thought these two looked nicer separately, but let me know if you want them in a single graph
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Split combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
	legend pos=north west,
]
\addplot coordinates {(1,9) (2,27) (3,40) (4,53) (5,66) (6,79) (7,92)
  % Last bar doesn't show for some reason, so need to add a dummy value for the next one
    (8,1) };

@@

\end{axis}
\end{tikzpicture}
\end{minipage}
\begin{minipage}[t]{0.10\textwidth}
\quad
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
% Hide the label on the second graph
%	ylabel=Process states,
	xlabel=Pipelined combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
	legend pos=north west,
]
\addplot coordinates {(1,9) (2,17) (3,27) (4,37) (5,47) (6,57) (7,67)   (8,1) };

@@

\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Number of merges,
%  ymode=log,
  ymin=0, ymax=1500,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=6.5cm,
	legend pos=north west,
]
% These are the values for splitting.
% They are smaller than the 'chaining', but look much nicer on the linear graph.
\addplot coordinates {(1,9) (2,42) (3,97) (4,196) (5,383) (6,746) (7,1461)
  % (8,2880)
  (8,1)
  };

>>>>

% I thought these two looked nicer separately, but let me know if you want them in a single graph
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Split combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(1,9) (2,27) (3,40) (4,53) (5,66) (6,79) (7,92)
  % Last bar doesn't show for some reason, so need to add a dummy value for the next one
    (8,1) };

@@

\end{axis}
\end{tikzpicture}
\end{minipage}
\begin{minipage}[t]{0.10\textwidth}
\quad
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{tikzpicture}
\begin{axis}[
% Hide the label on the second graph
%	ylabel=Process states,
	xlabel=Pipelined combinators,
  ymin=0, ymax=100,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(1,9) (2,17) (3,27) (4,37) (5,47) (6,57) (7,67)   (8,1) };

@@

\begin{tikzpicture}
\begin{axis}[
	ylabel=Process states,
	xlabel=Number of merges,
%  ymode=log,
  ymin=0, ymax=1500,
	enlargelimits=0.01,
	ybar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
% These are the values for splitting.
% They are smaller than the 'chaining', but look much nicer on the linear graph.
\addplot coordinates {(1,9) (2,42) (3,97) (4,196) (5,383) (6,746) (7,1461)
  % (8,2880)
  (8,1)
  };
